R for Clinical Study Reports and Submission

### 2021-10-27 slides/workshop-slides.Rmd
reorg r2rtf examples

@@

## r2rtf Motivation

@@

@@

@@

- Generate highly customized tables
- Limit package dependency
- Target regulatory deliverables   
- Support pipes (`%>%`)

- `r2rtf` Introduction: https://r4csr.org/overview.html#r2rtf

>>>>

```{r}
library(dplyr)
library(tidyr)
library(r2rtf)
```

@@

# r2rtf Introduction

## Motivation

@@

- [ICH E3 Structure and Content of Clinical Study Reports](https://database.ich.org/sites/default/files/E3_Guideline.pdf)

@@

- `r2rtf` is an R package to create production-ready tables and figures in RTF format.
The R package is designed to

@@

- provide simple "verb" functions that correspond to each component of a table, 
  to help you translate a data frame to a table in RTF file.
- enable pipes (`%>%`). 
- only focus on the **table format**. 
  Data manipulation and analysis shall be handled by other R packages. (e.g. `tidyverse`)

## Workflow

Before creating an RTF table we need to:

- Figure out table layout.

- Split the layout into small tasks in the form of a computer program.

- Execute the program.

## Minimal Example

`r2rtf` is designed to enable pipes (`%>%`)

```{r, echo = TRUE, eval = FALSE}
head(iris) %>%
  rtf_body() %>%                     # Step 1 Add table attributes 
  rtf_encode() %>%                   # Step 2 Convert attributes to RTF encode 
  write_rtf("minimal.rtf")           # Step 3 Write to a .rtf file
```

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("minimal.pdf")
```

## Package Overview

`r2rtf` package provides the flexibility to customize table appearance for

- **Table component**: title, column header, footnote, etc.
- **Table cell style**: size, border type, color, font size, text color, alignment, etc.
- **Flexible control**: the specification of the cell style can be row or column vectorized.
- **Complicated format**: pagination, section grouping, multiple table concatenations, etc.

`r2rtf` package also provides the flexibility to convert figures in RTF format.

## Simple Example - Adverse Events

`r2rtf` only focuses on **table format**. 
Data manipulation and analysis shall be handled by other R packages. (e.g. `tidyverse`)

- Let's refer examples in the [Section 2.4.2](https://r4csr.org/overview.html#r2rtf)

## Function Summary

`r2rtf` provides simple "verb" functions that correspond to each component of a table, 
  to help you translate data frame to table in RTF file.

```{r, echo = FALSE}
r2rtf_funs <- read.csv("r2rtf-functions.csv")
names(r2rtf_funs)[3] <- "Optional/required"
knitr::kable(r2rtf_funs)
```

## Function Illustration

```{r, out.width="80%", echo = FALSE}
knitr::include_graphics("function_summary.PNG")
```

# CSR Examples
